Weather Data Integration and Assimilation System\\

### 2020-02-10 method/sec_3-microservice.tex
K8s intro

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
    \caption{\acrfull{k8s} architecture.}
    \label{fi:k8s_architecture}
\end{figure}

- Explain how k8s support microservice architecture

>>>>

\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}. It groups containers that make up an application into logical units for easy management and discovery.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
    \caption{\acrfull{k8s} architecture.}
    \label{fi:k8s_architecture}
\end{figure}
Components of \acrshort{k8s},
\begin{itemize}
    \item Pods – Cluster of containers that can group other container images in a single unit.
    \item Nodes - the machines (VMs, physical servers, etc) in a cluster that run your applications and cloud workflows.
    \item kubelet - An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
    \item kube-proxy - A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
    \item Kubernetes master - Responsible for maintaining the desired state for your cluster.
    \item etcd - Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
\end{itemize}
Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy application as pods into cluster nodes.
Each microservice can deploy as a Pod which is a group of containerize applications. And \acrshort{k8s} able to scale as much as user want as described above.
